Analysis

### 2021-12-17 code/R/Analysis.Rmd
Parameter testing

>>>>

parameterTest_3
```{r}
d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_NYAA-04_Evaluate.csv")

d1 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

```
```{r}
# NYAA-04 gt:
nyaa04_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2021_12_13_NorwayAnnotations_NYAA-04_IndividualAnnotations_FRCNN_Metrics.csv")

length(unique(nyaa04_gt$id_gt))

```
```{r}
# Minimum mm: 10,300,60-70,29,0.9835414,38
# All zero: 0,0,0,68,0.9614075,31
# Correct noo with minimum mm:  70-160,800-1000,10,36,0.9795687,21

minmm = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NYAA-04_3/parameterTest_NYAA-04_maxDisap_10_runMean_60_maxDist_300.csv")

allzero = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NYAA-04_3/parameterTest_NYAA-04_maxDisap_0_runMean_0_maxDist_0.csv")

cornoo = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NYAA-04_3/parameterTest_NYAA-04_maxDisap_70_runMean_10_maxDist_800.csv")
